Dissertation Proposal

### 2023-11-07 proposal.tex
the SMoL Lang

SMoL's Lispy syntax is
an artifact of the course (\Cref{s:populations}) using Racket
\citep{friedmanEssentialsProgrammingLanguages2001, krishnamurthiProgrammingLanguagesApplication2007};
however, it also proved to be pedagogically valuable.
I have found the parentheses useful when discussing
scope in conjunction with local-binding features like \lstinline|let|.
This avoids the various confusing ``variable lifting'' semantics found
in languages like Python (\cite{politzPythonFullMonty2013}; see also
posts like \cite{froadieWhatScopeVariable2022}), where the actual defined range of a
variable is not apparent from the source code.

Nevertheless, most SMoL programs are easy to translate to other
languages. I present machine-translated Python and JavaScript
versions of our programs in \supplRef{Translated\_Programs.html}. Furthermore, we intend to
make a multi-lingual tutor in the future (\Cref{s:future-work}).

>>>>

SMoL defines a semantic but not the syntax. However, to repsent SMoL
to students, I have to choose a syntax. I chose a Lispy syntax, which
is an artifact of the major population where I conducted studies: a
course (\Cref{s:populations}) using Racket
\citep{friedmanEssentialsProgrammingLanguages2001,
krishnamurthiProgrammingLanguagesApplication2007}. However, the Lispy
syntax also proved to be pedagogically valuable. I have found the
parentheses useful when discussing scope in conjunction with
local-binding features like \lstinline|let|. This avoids the various
confusing ``variable lifting'' semantics found in languages like
Python (\cite{politzPythonFullMonty2013}; see also posts like
\cite{froadieWhatScopeVariable2022}), where the actual defined range
of a variable is not apparent from the source code.

Nevertheless, most SMoL programs are easy to translate to other
languages. I present machine-translated Python and JavaScript versions
of my programs in \supplRef{Translated\_Programs.html}. Furthermore, I
intend to make a multi-lingual tutor in the future
(\Cref{s:future-work}).
